---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #b3a7fe;
  padding: 10px;
}
h2 {
  font-family: "Fontspring Demo - Palo Slab Condensed", serif;
  font-size: 5vw
}
h1, h3, h4, h5, h6 {
  font-family: "Fontspring Demo - Palo Slab Condensed", serif;
  font-size: 2vw;
}
p {
 font-family: "Arial";
 font-size: 1.5vw;
}
```

## How difficult is the New York Times Games' Connections puzzle?

The NYT Games' Connections puzzle is a puzzle that is solved by finding four groups of related terms from a total pool of sixteen. The solved categories are colour coded by order of difficulty: yellow, green, blue, and purple. The difficulty of the puzzle varies from day to day. In this report, I analyse data from my Connections puzzle solves.

### Plots:
```{r}
library(tidyverse)
library(magick)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQn3Ws29VdvufJUpnuFuptZ77C2azIcFiMMSy3vGaVJhW28OiEgAw8qosl6rthchoyrqyJeRWraTZF2/pub?output=csv") 

# rename variables for readability
latest_data <- logged_data %>%
  rename(timestamp = 1,
         number_of_mistakes = 2,
         first_category = 3,
         personal_difficulty = 4,
         true_difficulty = 5,
         time_taken = 6)

# summary values
average_time_taken <- round(mean(latest_data$time_taken), 0)
average_personal_difficulty <- round(mean(latest_data$personal_difficulty), 0)
average_true_difficulty <- round(mean(latest_data$true_difficulty), 0)
total_number_of_responses <- nrow(latest_data)

# plot 1 (difficulty)
difficulty_data <- latest_data %>%
  select(personal_difficulty, true_difficulty)

difficulty_data_sorted <- difficulty_data %>%
  mutate(personal_difficulty = paste0("personal_difficulty=", personal_difficulty),
         true_difficulty = paste0("true_difficulty=", true_difficulty)) %>%
  mutate(combined_types_of_difficulties = paste(true_difficulty, personal_difficulty, sep = ",")) %>%
  select(combined_types_of_difficulties) %>%
  separate_rows(combined_types_of_difficulties, sep = ",") %>%
  separate(combined_types_of_difficulties, into = c("difficulty_type", "difficulty_value"), sep= "=") %>%
  mutate(difficulty_value = factor(difficulty_value, levels = c("1", "2", "3", "4", "5")))

sorted_difficulty_plot <- ggplot(difficulty_data_sorted, aes(x = difficulty_value, fill = difficulty_type)) +
  geom_bar(position = "dodge") +
  labs(title = "Was it really that difficult?",
       subtitle = "Comparing the frequency of personal and true difficulty ratings of Connections puzzles",
       x = "Difficulty rating",
       y = "Number of solves",
       fill = "Type") +
  scale_fill_manual(values = c("personal_difficulty" = "#b1c4ef",
                               "true_difficulty" = "#ba81c5")) +
  theme(plot.title = element_text(family = "Fontspring Demo - Palo Slab Condensed"))

# print plot
sorted_difficulty_plot

# plot 2 (time)
time_taken_sorted <- latest_data %>%
  mutate(
    time_group = cut(
      time_taken,
      breaks = c(0, 30, 60, 90, 120, 150, 180, Inf),
      labels = c("0-30", "31-60", "61-90", "91-120", "121-150", "151-180", "180+")
    )
  )

time_taken_plot <- ggplot(data = time_taken_sorted) +
  geom_bar(aes(x = time_group, fill = first_category)) +
  labs(title = "How long does it take?",
       subtitle = "Comparing the time taken to complete a Connections puzzle with the first category \nsolved",
       x = "Time in seconds",
       y = "Number of solves",
       fill = "Categories") +
  scale_fill_manual(values = c("Yellow" = "#f9df6e",
                               "Green" = "#a0c45a",
                               "Blue" = "#b1c4ef",
                               "Purple" = "#ba81c5")) +
  theme(plot.title = element_text(family = "Fontspring Demo - Palo Slab Condensed"))

# print plot
time_taken_plot

# get Connections example image
example_image1 <- image_read("https://static01.nyt.com/images/2023/08/27/multimedia/27-THE-MORNING-NL--02/27-THE-MORNING-NL--02-articleLarge-v2.jpg?quality=75&auto=webp&disable=upscale") %>%
  image_scale(400)
example_image2 <- image_read("https://static01.nyt.com/images/2023/08/25/admin/oakImage-1692973708926/oakImage-1692973708926-superJumbo.jpg") %>%
  image_scale(400)

```

### Summary values:
The above graphs were generated using **`r total_number_of_responses`** data points.

The average time taken to solve a puzzle was **`r average_time_taken`** seconds.

The average *perceived* difficulty of a puzzle was **`r average_personal_difficulty`** whereas the average *actual* difficulty of a puzzle was **`r average_true_difficulty`**.

### Example images of the game for your understanding:
`r example_image2` `r example_image1`
